CSD, Disjoint components and trayectory detection

### 2017-11-01 ArticuloCSDyCM/Paper03.tex
cambios menores

Spatially tracking the activity of electro-physiological data in a concise, rigorous and interpretable manner poses a challenging problem. Measurement recordings are usually presented first as a series of traces that correspond each to a sampling point in the studied structure. As Micro Electrode Arrays (MEAs) become denser, this representation of the data becomes saturated and the discovery of patterns turns into a difficult task. Novel information is obfuscated by the same high density acquisition that allows us to discover it. Therefore, representing  the recorded data in ways which can unveil previously unobtainable information is a necessity. Various techniques for separation of functional generators are available now, most come from the application of blind source separation analysis, such as ICA. 
Our task in this paper is to present a method for tracing out ``functional connectivity'', which would bring independent information that is complementary to those analysis.  Our  method would be applicable mostly to activity in structured neural tissue. We shall exemplify it by application to the data obtained from recordings of the rats hippocampus.

>>>>

Spatially tracking the activity of electro-physiological data in a concise, rigorous and interpretable manner poses a challenging problem. Measurement recordings are usually presented first as a series of traces that correspond each to a sampling point on the tissue. As Micro Electrode Arrays (MEAs) become denser, this representation of the data becomes saturated and the discovery of patterns turns into a difficult task. Novel information is obfuscated by the same high density acquisition that allows us to discover it. Representing  the recorded data in ways which can unveil previously obfuscated information is a necessity. Various techniques for separation of functional generators are available now, most come from the application of blind source separation analysis, such as ICA. 
Our task in this paper is to present a method for tracing out ``functional connectivity'', which would bring independent information that is complementary to those analysis.  Our  method would be applicable mostly to activity in structured neural tissue. We shall exemplify it by application to the data obtained from recordings of the rats hippocampus.
